### 2015-02-22 fundamentals/intro.tex
Fix a couple of typos

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor,
\gls{GENIUS} Version 1 \cite{dunzik-gougar_global_2007,jain_transitioning_2006},
originated within \gls{INL} and sought to provide generic regional capability.
Based on lessons learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version
2 \cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
generality and an extensible interface to facilitate collaboration.  The
\Cyclus project then improved upon the \gls{GENIUS} effort by
implementing increased modularity and encapsulation.  The result is a dynamic
simulator that treats both materials and facilities discretely, with an
architecture that permits multiple and variable levels of fidelity. The
simulator's agent-based framework for tracking the transformation and tradef
resources between autonomous regional and institutional entities with
customizable behavior and objectives is an innovation not pursued by any
existing fuel cycle simulator.

@@

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community. This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives, and was attained by the \emph{modular and open architecture} of
\Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
methodologies with \emph{agent interchangeability}.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators.  due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.

>>>>

\Cyclus emerged from a line of tools seeking to break this practice.  Its
precursor,
\gls{GENIUS} Version 1 \cite{dunzik-gougar_global_2007,jain_transitioning_2006},
originated within \gls{INL} and sought to provide generic regional capability.
Based on lessons learned from \gls{GENIUS} Version 1, the \gls{GENIUS} Version
2 \cite{oliver_studying_2009,huff_geniusv2_2009} simulator sought to provide more
generality and an extensible interface to facilitate collaboration.  The
\Cyclus project then improved upon the \gls{GENIUS} effort by
implementing increased modularity and encapsulation.  The result is a dynamic
simulator that treats both materials and facilities discretely, with an
architecture that permits multiple and variable levels of fidelity. The
simulator's agent-based framework for tracking the transformation and trade of
resources between autonomous regional and institutional entities with
customizable behavior and objectives is an innovation not pursued by any
existing fuel cycle simulator.

@@

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community. This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives, and was attained by the \emph{modular and open architecture} of
\Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
methodologies with \emph{agent interchangeability}.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators, due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.
